Quantifying the number of *rrn* operons across taxonomic ranks

### 2020-10-05 exploratory/2020-10-05-rrn-copy-number.Rmd
Fix line breaks in plot title

rank_taxon_rrns %>%
	ggplot(aes(x=rank, y=mean_rrns)) + 
	geom_jitter(width=0.3, alpha=0.3) +
	theme_classic() +
	labs(x=NULL, 
			 y="Mean number of rrn copies per genome",
			 title="There is wide variation at the species\nlevel in the number of rrn copies",
			 subtitle="Each point represents a single taxon\nwithin that rank, numbers based on\nan average species copy number")
```

>>>>

rank_taxon_rrns %>%
	ggplot(aes(x=rank, y=mean_rrns)) + 
	geom_jitter(width=0.3, alpha=0.3) +
	theme_classic() +
	labs(x=NULL, 
			 y="Mean number of rrn copies per genome",
			 title="There is wide variation at the species level in the number of rrn copies",
			 subtitle="Each point represents a single taxon within that rank, numbers based on\nan average species copy number")
```
